Plant-pollintor networks worldwide are composed by the same specific building

### 2021-10-05 Draft/Draft.Rmd
Caption of figure 5 and edits on results

Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions (i.e., the mediated effect between two species by a third species), such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008]. Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., interaction frequency) or in single topological indices (e.g., nestedness). Nonetheless, the emerging framework of network motifs in plant-pollinator research, the building blocks of a network that depict subsets of interactions [@milo2002], allows to consider both direct and indirect interactions [@simmons2019]. The analysis of motifs (meso-scale) in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020]. Yet, the global patterns of indirect interactions in plant-pollinator networks (over- and under- represented motifs) are still unknown.

@@

We calculated which functional groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts. We extracted the position frequencies of all motifs from three to five nodes for each network and species by using the _bmotif_ package [@bmotifsimmons2019]. To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure for each group by the total number of times that a group appears in any position within the same motif size class. Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did with motif frequencies. To outline the general patterns of position frequencies across networks and functional groups, we fit a LMM per motif position, where the response variable was the observed position percentile per network. We used the functional group identifier as an explanatory variable and the study identifiers as a random intercept. By adding the functional group estimates to the model intercept, we assessed the average motif frequency, after controlling the variation at the study level. Finally, we visualized with the help of the package ComplexHeatmap version 2.6.2 [@gu2016] over- and under- representation of plant and pollinator functional groups on the different motif positions.

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of motif frequencies between empirical and simulated networks divided by average path length (plots a, b, c and d) as determined in Simmons et al. (2020). This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles). This was done by network (light blue dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
library(lme4)
library(nlme)
library(tidyverse)
source("../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
d <- add_study_id(d)
#str(d)
#head(d)

@@

Although motifs positions determined over- and under- representation independently of the identity of functional groups for most cases (rows in **Figure 3**), we found differences in the average percentile within floral visitors and pollinators functional groups (columns in **Figure 3**). These differences were more marked for floral visitors functional groups. The group of Bees was the most over-represented, followed by non-syrphids Diptera, syrphids, Coleoptera, non-bee hymenoptera and finally Lepidoptera which was the most under-represent functional group on the different motif positions. Although for plants the differences across groups were less pronounced, from most represented functional group on the different motif positions to lowest we found self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions. The different motif positions are dividied by the average path length clasification determined by Simmons et al. (2020)."}

@@

The different observed frequencies on the different motif positions showed a hirarchical order of probabilities for floral visitors (**Figure 4**). That is, the functional group of 'bees' was the most abundant one on all motif positions followed by non-syrphid Diptera which was after bees, the second most frequent functional group on all positions. Then, the group of syrphids was the most abundant in all positions but two (positions 28 and 31 from motifs 11 and 12, respectively). After syrphids, Coleoptera was the most frequent group on the different positions followed by non-bee Hymenoptera and finally, Lepidoptera which was the less frequent group on all positions but two (positions 12 and 22 from motifs 5 and 9, respectively). Remarkably, plant functional groups were more variable on the different motif positions. However, there were also predominant functional groups found across the different motif positions. The three most frequent groups were 'tall plants with small unisexual flowers', 'self-incompatible perennials with large flowers' and 'small outcrossing perennials'. On the contrary, the groups of 'selfing herbs' and 'short lived outcxrossers with long zygomorphic flowers' had the lowest probability to be present on the different motifs plant positions.

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.**"}

>>>>

Traditionally, plant-pollinator research has focused on direct interactions but overlooked indirect interactions (i.e., the mediated effect between two species by a third species), such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008]. Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g., interaction frequency) or in single topological indices (e.g., nestedness). Nonetheless, the emerging framework of network motifs in plant-pollinator research, the building blocks of a network that depict subsets of interactions [@milo2002], allows to consider both direct and indirect interactions [@simmons2019]. The analysis of motifs on this intermediate level of complexity (meso-scale) in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020]. Yet, the global patterns of indirect interactions in plant-pollinator networks are still unknown (e.g., over- and under- represented motifs).

@@

We calculated which functional groups were over or under-represented in different motif positions by comparing position frequencies of empirical networks with those of their corresponding simulated counterparts. We extracted the position frequencies of all motifs from three to five nodes for each network and species by using the _bmotif_ package [@bmotifsimmons2019]. To estimate the position frequencies of each functional group in a given network, we added the frequencies of those species that belong to the group, and then, we normalised the resulting frequencies by dividing the position measure [Sum of position frequencies?]() for each group by the total number of times that a group appears in any position within the same motif size class. Then, we calculated the percentile of the observed position frequencies for each group and network, just like we did with motif frequencies. To outline the general patterns of position frequencies across networks and functional groups, we fit a LMM per motif position, where the response variable was the observed position percentile per network. We used the functional group identifier as an explanatory variable and the study identifiers as a random intercept. By adding the functional group estimates to the model intercept, we assessed the average motif frequency, after controlling the variation at the study level. Finally, we visualized with the help of the package ComplexHeatmap version 2.6.2 [@gu2016] over- and under- representation of plant and pollinator functional groups on the different motif positions.

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure 2.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al. (2020). This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles). This was done by network (light blue dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
library(lme4)
library(nlme)
library(tidyverse)
source("../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
d <- add_study_id(d)
#str(d)
#head(d)

@@

The comparison of the frequencies between the positions of motifs of empirical and simulated networks showed that motifs positions determined over- and under- representation independently of the identity of functional groups for most cases (rows in **Figure 3**). However, we also found differences in the average percentile within floral visitors and plant functional groups on the different motif positions (columns in **Figure 3**). These differences were more marked for floral visitors functional groups, and thus the groupings by average path length were less informative for floral visitors than for plants. In other words, for plants motifs by themselves were more descriptive than for floral visitors. From most over- to under-represented floral visitors functional groups, we found: bees, non-syrphids Diptera, syrphids, Coleoptera, non-bee hymenoptera and Lepidoptera. Although plant functional groups showed less differences between them, there were also more represented functional groups than others, thus from most over- to under-represented groups on the different motif positions we found: self incompatible perennials with large flowers, small outcrossing perennials, tall plants with unisexual flowers, selfing herbs and short lived outcrossers with long zygomorphic flowers.

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', out.width="95%",fig.cap="\\textbf{Figure 3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions. The different motif positions are dividied by the average path length clasification determined by Simmons et al. (2020)."}

@@

The different observed frequencies on the different motif positions showed a hirarchical order of probabilities for floral visitors (**Figure 4**). That is, the functional group of 'bees' was the most abundant one on all motif positions followed by non-syrphid Diptera which was after bees, the second most frequent functional group on all positions. Then, the group of syrphids was the most abundant in all positions but two (positions 28 and 31 from motifs 11 and 12, respectively). After syrphids, Coleoptera was the most frequent group on the different positions followed by non-bee Hymenoptera and finally, Lepidoptera which was the less frequent group on all positions but two (positions 12 and 22 from motifs 5 and 9, respectively). Remarkably, plant functional groups were more variable on the different motif positions. However, there were also predominant functional groups found across the different motif positions. The three most frequent groups were 'tall plants with small unisexual flowers', 'self-incompatible perennials with large flowers' and 'small outcrossing perennials'. On the contrary, the groups of 'selfing herbs' and 'short lived outcrossers with long zygomorphic flowers' had the lowest probability to be present on the different motifs plant positions.

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=8, fig.width=12, fig.cap="**Figure 5.** Z-score comparison (95% confidence level) of the observed and expected frequencies motif combinations with four specific graphical examples of the most probable motifs of being observed for each category delimitid by the z-score critical values: under-represented, no statistical difference and over-represented."}
